Patient-Specific Neural Field Modeling from Micro-Electrode Data

### 2010-07-26 ltx/data_paper/DataPaper.tex
changed notation in EM
added parameters on expectation for Xi1 and Xi4

&&-\boldsymbol\theta^\top q(\mathbf x_t)^\top\boldsymbol\Sigma_e^{-1}q(\mathbf x_t)\boldsymbol\theta-2\xi \mathbf x_t^\top\boldsymbol\Sigma_e^{-1}q(\mathbf x_t)\boldsymbol\theta-\xi^2\mathbf x_t^\top\boldsymbol\Sigma_e^{-1}\mathbf x_t.

@@

&&-\boldsymbol\theta^\top q(\mathbf x_t)^\top\boldsymbol\Sigma_e^{-1}q(\mathbf x_t)\boldsymbol\theta-2\xi \mathbf x_t^\top\boldsymbol\Sigma_e^{-1}q(\mathbf x_t)\boldsymbol\theta-\xi^2\mathrm{tr}\left\lbrace \mathbf x_t \mathbf x_t^\top\boldsymbol\Sigma_e^{-1}\right\rbrace. 

@@

Now taking the expectation of the log likelihood function gives the $\mathcal Q$-function, which is the lower-bound that needs to be maximised to gain optimal parameter estimates. The $\mathcal Q$-function is written as  

@@

\Xi_1&=\mathbf E\left[\sum_{t=1}^T\mathbf x_t\mathbf x_{t+1}^\top\right] \\

@@

 \Xi_4&=\mathbf E\left[\sum_{t=1}^T\mathbf x_t\mathbf x_{t}^\top\right]

>>>>

&&-\boldsymbol\theta^\top q^\top(\mathbf x_t)\boldsymbol\Sigma_e^{-1}q(\mathbf x_t)\boldsymbol\theta-2\xi \mathbf x_t^\top\boldsymbol\Sigma_e^{-1}q(\mathbf x_t)\boldsymbol\theta-\xi^2\mathbf x_t^\top\boldsymbol\Sigma_e^{-1}\mathbf x_t.

@@

&&-\boldsymbol\theta^\top q^\top(\mathbf x_t)\boldsymbol\Sigma_e^{-1}q(\mathbf x_t)\boldsymbol\theta-2\xi \mathbf x_t^\top\boldsymbol\Sigma_e^{-1}q(\mathbf x_t)\boldsymbol\theta-\xi^2\mathrm{tr}\left\lbrace \mathbf x_t \mathbf x_t^\top\boldsymbol\Sigma_e^{-1}\right\rbrace. 

@@

Now taking the expectation of the log likelihood function for all time instants gives the $\mathcal Q$-function, which is the lower-bound that needs to be maximised to gain optimal parameter estimates. The $\mathcal Q$-function is written as  

@@

\Xi_1&=\mathbf E_{(\theta',\xi')}\left[\sum_{t=1}^T\mathbf x_t\mathbf x_{t+1}^\top\right] \\

@@

 \Xi_4&=\mathbf E_{(\theta',\xi')}\left[\sum_{t=1}^T\mathbf x_t\mathbf x_{t}^\top\right]
